% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
\usepackage{hyperref}
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\newcommand{\companyName}{Company Name}

\begin{document}

%\signature{Mike Dalton}
%\longindentation=0pt                       % needed to get closing flush left
%\let\raggedleft\raggedright                % needed to get date flush left

\begin{flushleft}
{\large\bf Mike Dalton}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill michaelcdalton@gmail.com \\
\end{flushright}

Hello,

I am reaching out to you because I am interested in your software engineering position. I've spent the last 2 years working with Java and prior to that spent 4 years working with Ruby on Rails. I consider myself a problem solver and I'm at my best when I'm solving challenging problems.

At my current position at Grubhub, I've been a member of two teams. As a member of the restaurant financials team, I've been working on migrating a legacy web service that calculates the fees for every order we receive. As a member of the delivery operations team, I worked on a React application that is used by our delivery operation specialists to manage the delivery drivers.

Previous to Grubhub, I was a senior software engineer at Zoomer, I was working on their product team developing two applications: a routing application and a UI for dispatchers. The routing application received orders from restaurants and determined the optimal pairings for those orders and drivers that are available to deliver those orders. The dispatcher UI was used by our dispatchers to give them a view of the drivers and orders and help them troubleshoot any problems that arose.

Previous to Zoomer, I was a technical lead on a project team at WebLinc. While at WebLinc, I lead development efforts on several sites including \url{https://jefferspet.com}, \url{https://www.idville.com} and \url{https://www.purepromo.com}. The development of these sites required constant communication with internal team members and the client. Most sites involved integrations with 3rd party fulfillment systems, payment gateways and email service providers.

I would love to set up a time for us to meet and discuss the role in more depth.

Sincerely,

Mike Dalton

\end{document}
