\documentclass[line]{style}
\usepackage{enumitem}

\sectionskip=2.5ex plus 1ex minus -.2ex % values stolen from LaTeX
\setlist[itemize]{leftmargin=*}

\begin{document}
\newsectionwidth{0in}

\name{Mike Dalton}
\address{michaelcdalton@gmail.com}
\address{linkedin.com/in/michaelcdalton}

\begin{resume}

\section{EXPERIENCE}

{\sl Lead Engineer} \hfill 2022 to Present \\
{\sl Senior Engineer} \hfill 2021 to 2022 \\
TriumphPay, Philadelphia, PA
\begin{itemize} \itemsep -2pt
\item Led team of engineers on development of our Audit product which is built with Ruby on Rails, Elm and React.
\item Decreased customer onboarding time for our new Payments Network product by automatically integrating our existing customers that are using our Audit product.
\item Developed data lake using AWS, Terraform and Python which centralizes data across our databases and integrations allowing for our business analysts to build reports.
\end{itemize}

{\sl Engineering Manager} \hfill 2020 to 2021 \\
{\sl Senior Software Engineer} \hfill 2017 to 2020 \\
GrubHub, Philadelphia, PA
\begin{itemize} \itemsep -2pt
\item Led accounting engineering team developing a service to process 1 million orders per day and pay 200,000 restaurants each week.
\item Generated ACH files that distribute \$500 million every month to 100,000 restaurants.
\item Integrated with Stripe to pay 10,000 restaurants on weekly basis.
\item Migrated accounting logic from a monolithic app to new micro-service based architecture.
\item Reduced the amount of time it took to recruit a driver by 5 days by automatically migrating the driver data from a 3rd party tool to our driver databases.
\item Developed React based scheduling app that allowed delivery drivers to request their own schedule.
\end{itemize}

{\sl Senior Software Engineer} \hfill 2016 to 2017 \\
Zoomer Delivery, Philadelphia, PA
\begin{itemize} \itemsep -2pt
\item Collaborated with data scientists to build routing algorithms to pair delivery drivers with orders.
\item Built React application for dispatchers to manage drivers, restaurants and orders in real-time.
\end{itemize}

{\sl Technical Lead} \hfill 2013 to 2016 \\
WebLinc Commerce, Philadelphia, PA
\begin{itemize} \itemsep -2pt
\item Led development effort of e-commerce websites with more than \$20 million in annual revenue
\item Customized Rails-based WebLinc e-commerce platform to accommodate clients' needs
\item Integrated with payment gateways, email service providers and order management systems
\item Collaborated with project manager, user experience designer and client to determine requirements
\item Mentored developers transitioning from the legacy platform to the new Ruby on Rails platform
\end{itemize}

\section{SKILLS}
\begin{ncolumn}{3}
\begin{itemize} \itemsep -2pt
\item Ruby on Rails
\item Python
\item Java
\item Spring
\end{itemize}
&
\begin{itemize} \itemsep -2pt
\item PostgreSQL
\item Cassandra
\item MongoDB
\item ElasticSearch
\end{itemize}
&
\begin{itemize} \itemsep -2pt
\item JavaScript
\item React
\item Elm
\item CSS
\end{itemize}
\end{ncolumn}

\section{EDUCATION}
{\sl Master of Science in Computer Science} \hfill Expected 2023 \\
Georgia Institute of Technology, Atlanta, GA \\
GPA 4.0

{\sl Bachelor of Science in Computer Science,} Cum Laude \hfill 2011 \\
Drexel University, Philadelphia, PA \\
GPA 3.52

\end{resume}
\end{document}
